\documentclass[english,11pt,a4paper]{article}
\input{../Preamble}

\title{Handin 5}
\author{10893, Rasmus Bækgaard}
\date{September 27th, 2013}
\begin{document}
\maketitle

\section*{Problem 1}
\textbf{Consider the following statements:}
\\
$(1+2)^2-1^2=2^3\\
(1+2+3)^2-(1+2)^2=3^3\\
(1+2+3+4)^2-(1+2+3)^2=4^3$
\begin{enumerate}[a]
\item \textbf{Based on the three statement given above, what is the next statement suggested by these?}
\item[] $(1+2+3+4+5)^2-(1+2+3+4)^2=5^3$
\item \label{enu:1}\textbf{What conjecture is suggested by these statements?}
\item[] $(1+\ldots+n)^2-(1+\ldots+(n-1))^2=n^3$
\item \textbf{Verify the conjecture in (\ref{enu:1})}
\item[] 
\begin{align}
1+2+3+\ldots+n&=\dfrac{n(n+1)}{2}\\
\bigg(\dfrac{n(n+1)}{2}\bigg)^2-\Bigg(\dfrac{(n-1)\Big((n-1)+1\Big)}{2}\Bigg)^2
	&=\dfrac{1}{4}\Big(n^4+2n^3+n^2\Big)-\dfrac{1}{4}\Big(n^4-2n^3+n^2\Big)\\
	&=\dfrac{n^4+2n^3+n^2-n^4+2n^3-n^2}{4}\\
	&=\dfrac{4n^3}{4}\\
	&=n^3
\end{align}
\end{enumerate}



\section*{Problem 2}
\textbf{By an ordered partition of an integer $n \geq 2$ is meant a sequence of positive integers whose sum is $n$. For example, the ordered partition of 3 are $3,1+2,2+1,1+1+1$}
\begin{enumerate}[a]
\item \textbf{Determine the ordered partition of 4}
\item[] This gives 8 partitions:\\
$4, \\
1+3, 3+1, \\
2+2\\
1+1+2, 1+2+1, 2+1+1, \\
1+1+1+1$
\item \textbf{Determine the ordered partition of 5}
\item[] This gives 16 partitions: \\
$5, \\
1+4,4+1,\\
3+2,2+3,\\
3+1+1,1+3+1,3+1+1\\
1+2+2,2+1+2,2+2+1,\\
1+1+1+2,1+1+2+1,1+2+1+1,2+1+1+1,\\
1+1+1+1+1$
\item \textbf{Make a conjecture converting the number of ordered partition of an integer $n\geq 2$.}
\item[] For 3 it's 4 partitions, for 4 it's 8 partitions, for 5 it's 16 partitions.\\
This will be $n=2^{n-1}$
\end{enumerate}




\section*{Problem 3}
\textbf{Express the following quantified statement in symbols:}
\begin{enumerate}[a]
\item \textbf{\label{enu:3}For every odd integer $n$, the integer $3n+1$ is even:}
\item[]$\forall n, m \in \mathbb{Z}, n\%2 = 1: m = 3n+1 \Rightarrow m\%2=0$
\item \textbf{Prove that the statement in (\ref{enu:3}) is true.}
\item[] 
\begin{proof}

\begin{align}
n &= 2k+1\\
m &= 3n+1\\
	&=3(2k+1)+1\\
	&=6k+1+1\\
	&=2(3k+1)\\
	&=2a\label{equ:3}
\end{align}
From (\ref{equ:3}) we can see, that all odd integers gives an even number.
\end{proof}
\end{enumerate}



\section*{Problem 4}
\textbf{Express the following quantified statement in symbols}
\begin{enumerate}[a]
\item \label{enu:4}\textbf{There exists a positive even integer $n$, such that $3n+2^{n-2}$ is odd.}
\item[] This can be written as follow:
\begin{align}
\exists n, m \in \mathbb{Z}^+, n\%2=0 : m= 3n+2^{n-2} \Rightarrow m\%2=1
\end{align}
\item \textbf{Prove that the statement in (\ref{enu:4}) is true.}
\item[] To prove the statement in (\ref{enu:4}) is true, we write $n=2$:
\begin{align}
m &= 3\cdot 2+2^{2-2}\\
	&=6+2^0\\
	&=6+1\\
	&=7
\end{align}
\end{enumerate}



\section*{Problem 5}
\textbf{Prove or disprove: The sum of every five consecutive integers is divisible by 5 and the sum of no six consecutive integers is divisible by 6}
\\
\\
It can be written as follow:
\begin{align}
\dfrac{n+(n+1)+(n+2)+(n+3)+(n+4)}{5} 
	&=\dfrac{5n+10}{5}\\
	&=n+5 \\
\dfrac{n+(n+1)+(n+2)+(n+3)+(n+4)+(n+5)}{6}
	&= \dfrac{6n+15}{6} \\
	&= n\cdot \dfrac{15}{6} \label{equ:5}
\end{align}
From (\ref{equ:5}) we can see that it is not an integer.
Therefor the statement is false.


\section*{Problem 6}
\textbf{Consider the following statements:}
\\
$1=1, \\
1+3=4, \\
1+3+5=9, \\
1+3+5+7 = 16, \\
1+3+5+7+9=25$

\begin{enumerate}[a]
\item \textbf{Based on the three statements given above, what is the next statement suggested by these?}
\item[] $1+3+5+7+9+11 = 36$
\item \label{enu:6}\textbf{What conjecture is suggested by these statemets?}
\item[] $1+3+\ldots+(2n-1) = n^2$
\item \textbf{Verify the conjecture in (\ref{enu:6}) using induction.}
\item[] Lets check the base step and the induction step:
\begin{proof}

\begin{align}
1+3+\ldots+(2k-1) &= k^2 & P(k)\\
2\cdot 1-1&=1^2 & P(1) \\
1&=1 \label{equ:6-1}\\
1+3+\ldots+(2(k+1)-1) &= (k+1)^2 & P(k+1)\\
\underbrace{1+3+\ldots+(2k+1)}_{\mathclap{\text{This is P(k)}}}+2k+1 &= k^2+2k+1 & \text{Can be rewritten}\\
	k^2+2k+1 &= k^2+2k+1 \label{equ:6-2}
\end{align}
We see the base step (\ref{equ:6-1}) is equal and the induction step (\ref{equ:6-2}) is equal as well.
\end{proof}
\end{enumerate}



\section*{Problem 7}
\textbf{Using induction, prove that:}
\begin{enumerate}[a]
\item $\forall n \in \mathbb{N},\textbf{ if }n \geq 2, \textbf{then }n^3-n$ \textbf{is always divisible by 3}
\item[] 
\begin{proof}
Using the Method of Induction we show the base step and the induction step:
\begin{align}
\dfrac{k^3-k}{3} &= x & P(k),x \in \mathbb{N}\\
\dfrac{2^3-2}{3} &= x\\
\dfrac{6}{3} &= 2\label{equ:7-base} \\
\dfrac{(k+1)^3-(k+1)}{3} &= x \in \mathbb{N}\\
	&= \dfrac{k^3+3k^2+3k+1-k-1}{3} \\
	&= \underbrace{\dfrac{k^3-k}{3}}_{\mathclap{\text{P(k)}}}+\dfrac{3k^2+3k}{3} & P(k+1)\\
	&= x+k^2+k \label{equ:7-indu}
\end{align}
From the base step (\ref{equ:7-base}) we can see it is true, since $x$ is a natural number. 
The induction step is also true, since it (\ref{equ:7-indu}) is a natural number.
\end{proof}

\item $\forall n \in \mathbb{N}, n<2^n$
\item[]
\begin{proof}
Using the Method of Induction we show the base step and the induction step:
\begin{align}
k &< 2^k & P(k)\\
0 &< 2^0 & P(0)\\
0 &< 1 \label{equ:7-2-base}\\
\underbrace{k}_{P(k)}+1 &< 2^{k+1} & P(k+1)\\
2^k	+1 &< 2^k \cdot 2^1 \label{equ:7-2-indu}
\end{align}
We see the base step is true in (\ref{equ:7-2-base}) and the induction step is also true, shown in (\ref{equ:7-2-indu}).
\end{proof}
\end{enumerate}




\end{document}