\documentclass[oneside, 12pt]{article}

\include{Preamble}

\title{Assignment 4 --  Final reflections}
\author{Rasmus Bækgaard, 10893}
\date{January 3rd, 2015}

\begin{document}

\maketitle

The first play through  of the ME2 board game was interesting, since it was an undiscovered area it touched. 
This means it had the aspect of team play instead of the traditional "I must win" which put one in a new role, compared to the assumption for the game.

It also had very long rounds to which the thought of D\&D games came to mind -- achieve an unknown goal along with your companions. 
Each of you posses a different set of skills and you progress by rolling multiple dices. 
And with this is mind the game represent a real life situation where you can't predict you  teammates moves anymore than you can convince them of what the better path towards the unclear goal is, each member having their own vision of how to achieve this.

The team selected a different set of personalities and skill sets for the game, decided on the area of wearable technology, created a plausible story and thought we could implement microbots into the bloodstream. 
This served the purpose of letting the two bioprocess engineers have some sort of relation to the subject while the two electro engineers and the undersigned, computer engineer, could still contribute to the project.

As the game proceeded most of the group's member realized, that the idea of creating microbots was not for us and the game just had to end.
Even though we kept the time for the game, we didn't get very far as for what the score went and the game kept punishing us for not having creative types in the group which we, by deign of the game, needed badly for making microbots.
With that in mind we feared what would happen in round two, when only engineers remained.

In the following lesson the term \textit{disharmony} was introduced and we did a 5 minutes brainstorm on what annoyed us doing the day, chose the wireless digital key approach and tried to fill out the \textit{Business Model}.
This took 3 tries, since the market shifted from literally 'everything with a lock' to 'only homecare helpers' to 'if you have a door'. 
To solve the problem we brainstormed on all plausible ways to get a door open without actually touching it.
I got the idea to  rate every idea by different criteria, then weigh each criteria and sum the weighs for the most wanted solution. 
We thought of this as a splendid way of solving our problems, only slightly biased by the education of each member, and useful -- even though we ditched the idea and picked another as we did the Business Model rev. 3.
This was due to a key issue; our presentation revealed the population in general do not trust IT with screens, but have no problems with no-screen technology.

Practical thinking about how the user of the system would feel about taking the phone from their pocket to a door and back was not ideal, nor was always active Bluetooth good for the battery.
Using a key with energy harvesting, 2 meters range and an intelligent encryption, the product would not meet a lot of resident on the market.
This is classic effectuation -- we know something, we know what we potential can do with it and we know where we change the goal of what we will do based on this.

Applying the techniques in the ME2 game in round two gave us, surprisingly, a way better result, and we ended up on a score of about 8, instead of some-twenty from the first play through.
This showed us, that the methods used to create actual good, and useful, ideas is not just "lets make this", but requires a lot of thought, techniques, and planning.
The most surprising part for the group was the fact, that the business model could reveal some of the problems with the idea and relatively easy change the product, through the model, to be better for both the users, buyers and the company.

When working as a group, it's important to keep all participants excited about the project -- else you will lose them in the process.
Fortunately for us, we all had a certain amount of will and interest in the idea to accomplish something and create a solution for our disharmony. 
But as the original idea, microbots, changed to locks and hardware technology, one of the group's member became less and less engaged in the project.
This could luckily be solved by giving some fun tasks to that member and the more tedious tasks could be spread amongst the rest of the group.
Here, the part of leading the group is a job not easily handled, because group members does not have an obligation to actually take part in the process (however greatly appreciated).
\\
My own part in the group was neither leader, nor uninterested member, but rather realistic and presentation creative -- with this I mean a lot of the work for presenting the project was on my table.
When creating the business model I could see a lot of disadvantages with the idea, holes and direct stupidity in the design.
Addressing holes in an idea is never a popular trait, but presenting new solutions, fixes and modifications greatly ease it.

Due to time limitation the idea has the shape it has: Have a token in your pocket which opens locks within 2 meters. 
If you want it locked anyway you can click a button on the door to ignore the token until a new token arrives or you click the button again.
This is an OK solution but now you must remember to click the button if you token is just within the door (in your jacket or the likes).
It might be better to always lock doors when the token is on the inside and always let the inside be able to open the door.
But this, again, opens up for new disadvantages, so the product is not finished yet\dots at all.
\\
However -- the business model is good, it targets the correct consumers, challenges existing companies a way they must adapt to and gives us a few steps ahead of them.


\end{document}