\documentclass[danish, english]{article}
\input{Preamble}

\title{Lektion 2}
\begin{document}
\maketitle

\section*{1.4 The Matrix Equation $A\text{x}=b$}


\begin{theo}[En matrix equation]
\begin{ArgMat}
a & b & c\\
d & e & f
\end{ArgMat}
\begin{ArgMat}
x_1\\
x_2\\
x_3
\end{ArgMat} =
\begin{ArgMat}
\alpha\\
\beta
\end{ArgMat}

\end{theo}


\begin{theo}[Theorem 7] 
If A is an $m \times n$ matrix, with columns $a_1, \dots , a_n$, and if \textbf{b} is in $\mathbb{R}^m$, the \textbf{matrix equation}
\[Ax = b \]
has the same solution set as the \textbf{vector equation}
\[x_1a_1 + x_2a_2 + \dots + x_na_n = b \]
which, in turn, has the same solution set as the system of linear equations whose \textbf{augmented matrix} is\\
\centerline{
\begin{ArgMat}
a_1 & a_2 & \dots & a_n &b
\end{ArgMat}}

\end{theo}

\begin{theo}
The equation $A\textbf{x} = \textbf{b}$ has a solution if and only if \textbf{b} is a linear combination of the columns of $A$.
\end{theo}

A=\begin{ArgMat}
a_{l1} &a_{l2}&\dots&a_{ln}\\
\dots\\
a_{m1} &a_{m2}&\dots&a_{mn}
\end{ArgMat}=
\begin{ArgMat}
\vec{a_1}, \vec{a_2}, \dots, \vec{a_n}
\end{ArgMat}
\\
\\
$\vec{X}$ is  a vector in $\mathbb{R}^n$ \begin{ArgMat}
x_1\\
\dots\\
x_n
\end{ArgMat}
\\
\\
$A\vec{x}=$\begin{ArgMat}
x_1\\
\dots\\
x_n
\end{ArgMat}= $x_1\vec{a_1}+x_2\vec{a_2}+\dots+x_n\vec{a_n}$


\begin{theo}[Theorem 4] 
Let $A$ be $a_{nm} \times n$ matrix. Then the following statements are logically equivalent.
That is, for a particular $A$, either they are all true statements or they are all false.

\begin{enumerate}
\item For each b in $\mathbb{R}^m$, the equation $Ax = b$ has a solution.
\item Each b in $\mathbb{R}^m$ is a linear combination of the columns of A.
\item The columns of A span $\mathbb{R}^m$.
\item A has a pivot position in every row.
\end{enumerate}
\end{theo}
Eksempel:\\
A=\begin{ArgMat}
\vec{a_1} & \vec{a_2} & \vec{a_3} & \vec{a_4}
\end{ArgMat}=
\begin{ArgMat}
1 & 4 & 2&1\\
1&1&3&3\\
0&0&0&0
\end{ArgMat}
\\
\begin{enumerate}
\item No, Choose $\vec{b}$ =
\begin{ArgMat}
\alpha\\
\beta\\
\neq 0
\end{ArgMat}

\item No, Choose $\vec{b}$ =
\begin{ArgMat}
\alpha\\
\beta\\
\neq 0
\end{ArgMat}

\item Can't get a $\vec{x_3}$ direction (det skal være i 3 dimensioner)

\item Pivot is not in every row. (Check med MatLab: \textit{rref(A)})
\end{enumerate}

 

\section*{1.5 Solution Sets of Linear Systems}

\begin{theo} 
$A\vec{x}=\vec{0}$ -- Homogen equation(zero) -- $\vec{x} = \vec{0}$ er altid en solution, også kaldt "trivial solution".\\
$A\vec{x}=\vec{b}$ -- Inhomogen equation
\end{theo}


Eksempel:\\
\begin{align*}
3x_1+5x_2-4x_3 = 0\\
-3x_1-2x_2+4x_3=0\\
6x_1+x_2-8x_3=0
\end{align*}
Skriv en \begin{ArgMat}
A &|&\vec{0}
\end{ArgMat} $\Rightarrow$
\begin{ArgMat}
3&5&-4&0\\
-3&-2&4&0\\
6&1&-8&0
\end{ArgMat} $\sim$
\begin{ArgMat}
1&0&-\dfrac{4}{3}&0\\
0&1&0&0\\
0&0&0&0
\end{ArgMat} $\Rightarrow$
\begin{ArgMat}
x_1\\
x_2\\
x_3
\end{ArgMat} = $x_3$
\begin{ArgMat}
\dfrac{4}{3}\\
0\\
1
\end{ArgMat}
\\
\\
Eksempel:\\
$5x_1+4_x2-x_3=0 \Rightarrow$
\begin{ArgMat}
A&|&0
\end{ArgMat}=
\begin{ArgMat}
5&3&-1&0
\end{ArgMat}$\sim$
\begin{ArgMat}
1&\dfrac{4}{5} & \dfrac{-1}{5}&|&0
\end{ArgMat}\\
Note -- ingen pivot i de to sidste (kun den første) $\Rightarrow$
\\
\begin{ArgMat}
x_1\\
x_2\\
x_3
\end{ArgMat}=
\begin{ArgMat}
\dfrac{-4}{5}x_2 + \dfrac{1}{5}x_3\\
x_2\\
x_3
\end{ArgMat}=$x_2$
\begin{ArgMat}
\dfrac{-4}{5}\\
1\\
0
\end{ArgMat}+$x_3$
\begin{ArgMat}
\dfrac{1}{5}\\
0\\
1
\end{ArgMat}





\section*{1.7 Linear Independence}
\begin{theo} 
\begin{itemize}
\item Hvis en span indeholder $\vec{0}$ er den \underline{altid} \textbf{dependant}.
\item Hvis du ikke kan skalere op og få samme en vektor er den \textbf{independant}
\item Hvis der er en free variable er den \textbf{dependant}
\end{itemize}

\end{theo}
\textbf{Indsæt definition}\\
\\

$\vec{v_1} = $\begin{ArgMat}
1\\
4\\
3
\end{ArgMat},
$\vec{v_2} =$
\begin{ArgMat}
2\\
3\\
5
\end{ArgMat},
$\vec{v_3} =$
\begin{ArgMat}
3\\
6\\
2
\end{ArgMat}
\\
Er \{$\vec{v_1} \vec{v_2} \vec{v_3}$\} linear independant?\\
\\
\begin{ArgMat}
\vec{v_1}&\vec{v_2}&\vec{v_3}
\end{ArgMat}
\begin{ArgMat}
x_1\\
x_2\\
x_3
\end{ArgMat}=$\vec{0} \rightarrow$
\begin{ArgMat}
1 &2&3&0\\
4&3&6&0\\
3&5&2&0
\end{ArgMat} $\sim \sim \sim$
\begin{ArgMat}
1 &0 &0&0\\
0&1&0&0\\
0&0&1&0
\end{ArgMat}
\begin{solu}
x_1 = 0 \\
x_2 = 0\\
x_3 = 0	\\
\end{solu}\\
Dette er den \underline{eneste} trivial solution. 
Den er derfor linear independant.




\end{document}