\documentclass[jou]{apa6}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{bibliography.bib}
\title{Sample APA-Style Document Using the \textsf{apa6} Package}
\author{Brian D. Beitzel}
\affiliation{SUNY Oneonta}
\leftheader{Beitzel}
\abstract{This demonstration paper uses the \textsf{apa6} \LaTeX\
class to format the document in compliance with the 6th Edition of
the American Psychological Assocation’s \textit{Publication Manual.}
The references are managed using \textsf{biblatex}.}
\keywords{APA style, demonstration}
\begin{document}
\maketitle
We begin with \textcite{Shotton1989}. We can also cite this work in
parenthesis, like this: \parencite{Shotton1989}.
A three-author paper \parencite[e.g.,][]{Lassen2006} lists all
three authors for the first citation, then only the first author
on all subsequent citations \parencite{Lassen2006}.
Note the use of five heading levels throughout this demonstration
Method section.
\section{Method}
\subsection{Participants}
We had a lot of people in this study.
\subsection{Materials}
Several materials were used for this project. Some of them were
already created for prior research.
\subsubsection{Paper-and-Pencil Instrument}
We used an instrument that we found to be highly successful.
\paragraph{Reliability}
The reliability of this instrument is extraordinary.
14
\paragraph{Validity}
We now discuss the validity of our instrument.
\subparagraph{Face validity} The face validity is exceptionally
strong. Everyone should be impressed.
\subparagraph{Construct validity} Also very strong.
\subsection{Design}
This section describes the study’s design.
\subsection{Procedure}
The procedure was fairly straightforward, yet required
attention to detail.
\section{Results}
Table \ref{tab:ComplexTable} contains some sample data. Our
statistical prowess in analyzing these data is unmatched.
\begin{table}[htbp]
\vspace*{2em}
\begin{threeparttable}
\caption{A Complex Table}
\label{tab:ComplexTable}
\begin{tabular}{@{}lrrr@{}} \toprule
Distribution type & \multicolumn{2}{l}{Percentage of} & Total number \\
& \multicolumn{2}{l}{targets with} & of trials per \\
& \multicolumn{2}{l}{segment in} & participant \\ \cmidrule(r){2-3}
& Onset & Coda & \\ \midrule
Categorical -- onset\tabfnm{a} & 100 & 0 & 196 \\
Probabilistic & 80 & 20\tabfnm{*} & 200 \\
Categorical -- coda\tabfnm{b} & 0 & 100\tabfnm{*} & 196 \\ \midrule
\end{tabular}
\begin{tablenotes}[para,flushleft]
{\small
\textit{Note.} All data are approximate.
\tabfnt{a}Categorical may be onset.
\tabfnt{b}Categorical may also be coda.
\tabfnt{*}\textit{p} < .05.
\tabfnt{**}\textit{p} < .01.
}
\end{tablenotes}
\end{threeparttable}
\end{table}
\section{Discussion}
This is a lengthy and erudite discussion. It demonstrates amazing
15
skill in interpreting the results for the masses.
\printbibliography
\end{document}