##########################################################
List what CAN be explained - only do a few
##########################################################

1. Contents of a good specification

- Check that all parts match and everything is included
- Validate that stakeholders are happy (customer, user, developer)

- Write down business goals!
- Understandable for the customer
	- Word != meaning
	- Meaning != consequences for business
	- Show similar system/ pilot test.

- Correct: was that customer's actual need
- Unambiguous: Misunderstood
- Complete: Get all Non-trivial requirements written (Also get GUI in Task and Support)
- Consistent: No conflicts
- Verifiable: A "nice" user interface, isn't measurable.
- Modifiable: Categorize, prioritize and static labels in SRS
- Traceable: Forward and backward

- Describe data (Do CRUDO check on tasks vs. )
- Quality (performance, security, reliability, availability, interoperability, usability)
- ID on req.
- Risk assessment
- Tests
- Run through check list

(1)
Agenda:
- Stakeholders
- 7 checks
- Data
- Quality

Excellent:
- Structured + agenda
- Good with stakeholders
- Good with examples
- Good combination of practice and theory
- Good at keeping time
- Good body language

Remember:
- State it's an informal spec
- Happy stakeholders can't all be happy
- Requirement level, domain level
- Tendering process from proposal to ...
- Perspective / ref to checklist etc.
- CRUDO drawing
- Template for specs missing
- Write more on the board
- Verify must be "Verifyable"
- More references to other parts
- Short sentence


2. Discuss pros and cons with informal specification
- Define informal specs
- Template of IEEE (best pratice)
	- Use cases vs. tasks (when to use UC and when TD?)
- refer to Question 3

	Pros:
	- Natural language = user friendly (don't need pros)
	- Non-functional req. (GUI)
	- Domain-level and high-level can be expressed

	Cons: 
	- Natural language can be misunderstood
	- Validate and verify is much harder



3. Discuss pros and cons with formal specification
- What is formals  pec?
	- Elicitaion of req.
	- Example for critical system

- Pros and cons
	- What does this do for time spend?
	- Myth (Toyota uses it)

- Focus on model based techniques
	- ZDM-SL, Z, B
	- Mention other techniques
		- Logic base
		- Algebraic 

- Compare with informal spec Question 3
	- When to use what

- Compare to CGI guy



4. Relationships between assumptions, specifications and system properties

- Do examples with card tower
- Assumption + Specification => properties

- Thought it was ok if just 12 high (specification), but it could not be more than 14 (assumption)



- Assumption: 
	- Don't think you know it because it's not listed. Look out for requirements which are not explicid. 

- Specifications:
	- Listed 

- Properties:
	- Desired behaviour of the new system in the environment
	
- Elicitation techinique:
	- Pretotype for needs?

- Talk of formal and informal specification to verify you statements

- Move to Inspection types used for this:
	- Ad-hoc: Bring expert who can think of many issues for the system
	- Scenario: When the specs has been written




5. Compare different specification techniques
- Formal (Description + pros and cons)

- Informal (Description + pros and cons)
	-shall, should

- Use case (pros and cons)
	- They knwo what it is

- Task description (pros and cons)
	- They knwo what it is

- IEEE template (Tasks + pros and cons)

- Task Description(Ucs + pros and cons)





6. Reviewing and validating a specification
- Why important

- What a good spec?
	- 7 checks
- Ad-hoc
	- pros/cons
	- example
- Checklist
	- pros/cons
	- example
- Scenario
	- pros/cons
	- example
-CRUDO
- How inspection meetin is performed
- Review vs. inspection
- Formal specification
- Tendering
	




7. The tendering process using specifications

- Talk about picture SolIT01 p. 66
	- Talk about IEEE template and Søren Lauesen's task-description (Write specification)
		- Will formal or informal specs be best? (customer dependant)
	
- Talk about elicitation process
	- Do brainstorm
	- Send questions out for users
	- Do user interviews
	- Focus groups
	- Observation
	- Task demonstration
	- Domain workshop
	- Stakeholder analysis
	
- Puplic vs. private sector
		

	


8. Requirements elicitation (WAY OF FINDING!!!)
- Formulating the goal
	- How the elecitation process goes
	- Finding stakeholders

- Techniques:
	- interviews
	- stakeholders analysis
	- Observation
	- ... Question 7, step 2 and 3

- Relate to project

- Talk about picture SolIT01 p. 66


9. Formal VDM-SL specifications
- What is VDM-SL
- More than one langauge
- Example (SMALL) - the one you did
	- Data types
	- Functions
	- Operations
	- States
- Refer to Question 3 and 4



